\TheTitle

### 2019-12-16 Paper1/results.tex
added refinement barries for pipe
results minors

For the last numerical study we again use the Euler equations, but this time not in the context of the NACA airfoil, but rather with a bend Sod shock tube experiment. The prescribed initial condition for this testcase describes a gas at rest, but with a discontinuity, in density as well as energy in the upper part of the tube. The density $\rho_u = p/(R \cdot T)$ in the upper part is set to $\rho_u = 1.289$ with $p = 101\;325$ Pa, a temperature of $273.15$ K and the specific gas constant for dry air $R=287.87$. The energy $\rho e_u$ is set to exactly $1.0$. For the initial conditions in the lower part we set $\rho_l = 0.5 \cdot \rho_u$ and $\rho e_l = 0.3$. The heat capacity ratio $\gamma$ is set to $1.4$ as in the previous studies. We again augment the deterministic case by inflicting uncertainties and again increase the number uncertainties to three. The applied boundary conditions are Euler slip conditions $\bm{v}^T\bm{n}=0$ for the walls and Dirichlet type boundary conditions at the ends of the tube which set to the deterministic initial conditions. The first two uncertainties are the density and energy of the lower part of the shock tube. Here we set $\rho_l \sim U(1.189,1389)$ and $\rho e_l \sim U(0.2,0.4)$. The third uncertainty enters through the position of the shock itself and thus $y_\text{shock} \sim U(1.0, 1.2)$. Note, that in contrast to the upper testcases, here we are not interested in the steady state of the system, but rather the of time evolution of the expectancy and variance. The computational mesh (see Figure \ref{fig:referenceSolutionsPipeMesh}) is an unstructured mesh of $25\;458$ triangular cells, where the cells are all similar in size, i.e. there are not refined regions as in the NACA testcase. The simulations were run until a time of $2.0$s. The corresponding results can be seen in Figure \ref{fig:solution3D}. The reference solution in Figure \ref{fig:referenceSolutionsPipe1} and \ref{fig:referenceSolutionsPipe2} was computed using SC with 50 quadrature points in each stochastic dimension, yielding a total of $50^3=125\;000$ quadrature points.\\

@@

	\item It was not possible to obtain a result for sparse grids with moments of order 3 or higher. Any level up to level 11 ($72\;705$ quadrature nodes) of the used Clenshaw-Curtis sparse grids, resulted in a failure of the method during the computation of the mapping from the dual variables to the moment vector.

@@

	\item When using sparse grids with adaptivity the computational cost per quadrature node was observed to be smaller, showing that the nestedness property can potentially increase the methods performance.

>>>>

For the last numerical study we again use the Euler equations, but this time not in the context of the NACA airfoil, but rather with a bend Sod shock tube experiment. The prescribed initial condition for this testcase describes a gas at rest, but with a discontinuity, in density as well as energy in the upper part of the tube. The density $\rho_u = p/(R \cdot T)$ in the upper part is set to $\rho_u = 1.289$ with $p = 101\;325$ Pa, a temperature of $273.15$ K and the specific gas constant for dry air $R=287.87$. The energy $\rho e_u$ is set to exactly $1.0$. For the initial conditions in the lower part we set $\rho_l = 0.5 \cdot \rho_u$ and $\rho e_l = 0.3$. The heat capacity ratio $\gamma$ is set to $1.4$ as in the previous studies. We again augment the deterministic case by inflicting uncertainties and again increase the number uncertainties to three. The applied boundary conditions are Euler slip conditions $\bm{v}^T\bm{n}=0$ for the walls and Dirichlet type boundary conditions at the ends of the tube which set to the deterministic initial conditions. The first two uncertainties are the density and energy of the lower part of the shock tube. Here we set $\rho_l \sim U(1.189,1389)$ and $\rho e_l \sim U(0.2,0.4)$. The third uncertainty enters through the position of the shock itself and thus $y_\text{shock} \sim U(1.0, 1.2)$. Note, that in contrast to the upper testcases, here we are not interested in the steady state of the system, but rather the of time evolution of the expectancy and variance. The computational mesh (see Figure \ref{fig:referenceSolutionsPipeMesh}) is an unstructured mesh of $25\;458$ triangular cells, where the cells are all similar in size, i.e. there are not refined regions as in the NACA testcase. The simulations were run until a time of $2.0$s. For the refinement barries values of $\delta_{-} = 2\cdot 10^{-2}$ and $\delta_{+} = 4\cdot 10^{-3}$ were set for all adaptive simulations. The corresponding results can be seen in Figure \ref{fig:solution3D}. The reference solution in Figure \ref{fig:referenceSolutionsPipe1} and \ref{fig:referenceSolutionsPipe2} was computed using SC with 50 quadrature points in each stochastic dimension, yielding a total of $50^3=125\;000$ quadrature points.\\

@@

	\item It was not possible to obtain a result for sparse grids with moments of order 3 or higher. Any level up to level 11 ($72\;705$ quadrature nodes) of the used Clenshaw-Curtis sparse grids, resulted in an ill conditioned Hessian matrix of the dual problem and thereby to a failure of the method.

@@
